---
title: "ManyBabies Norming Analysis"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
library(dplyr)
library(knitr)
library(langcog)
library(ggplot2)
library(rjson)
library(readr)
library(stringr)
library(tibble)
library(purrr)
library(tidyr)
knitr::opts_chunk$set(echo = TRUE)
```

# Data loading and cleaning

Read in files and consolidate to the same directory. 

```{r warning=FALSE, error=FALSE, message=FALSE}
files <- dir("../production-results/")
d.raw <- tibble()

for (f in files) {
  jf <- paste("../production-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   rating = as.numeric(jd$answers$data$rating),
                   file = jd$answers$data$filename,
                   condition = jd$answers$data$condition,
                   age = jd$answers$data$age,
                   language = jd$answers$data$homelang,
                   race = jd$answers$data$race[1],
                   education = jd$answers$data$education,
                   children = jd$answers$data$children)
  d.raw <- bind_rows(d.raw, id)
}
```

Exclude non-compliant participants and non-English speakers. 

```{r}
compliant <- d.raw %>% 
  filter(grepl("choose", file)) %>%
  mutate(file = as.numeric(str_replace(str_replace(file, "\\.\\./choose_", ""), 
                            "\\.wav", ""))) %>%
  mutate(compliant = rating == file) %>%
  group_by(workerid) %>%
  summarise(compliant = mean(compliant) == 1)

english <- d.raw %>% 
  group_by(workerid, language) %>%
  distinct() %>%
  filter(str_detect(pattern = "[eE]nglish", language))

d <- d.raw %>%
  filter(workerid %in% compliant$workerid, 
         workerid %in% english$workerid, 
         !str_detect(file, pattern = "choose_"))
```

Merge in filename data. 

```{r warning=FALSE, error=FALSE, message=FALSE}
file_info <- read_csv("../wavs/file_key.csv")

d <- left_join(d, file_info)  
```

Distribution across conditions. 

```{r}
d %>% 
  group_by(condition, workerid) %>%
  distinct %>%
  group_by(condition) %>%
  summarise(n =n()) %>%
  kable
```

# Main analysis

Major summary histogram.

```{r}
d %>%
  mutate(object = !is.na(object)) %>%
  group_by(file, condition, register, object) %>%
  summarise(rating = mean(rating)) %>%
ggplot(aes(x = rating)) + 
  geom_histogram(binwidth=1) + 
  facet_grid(register~condition) + 
  theme_bw()
```

Check correlations between raters.

```{r}
d %>%
  split(.$condition) %>%
  map_df(function(x) {
    cors <- x %>% 
      select(workerid, rating, file) %>% 
      spread(workerid, rating) %>%
      select(-file) %>%
      cor
    cors[cors == 1] <- NA
    tibble(condition = x$condition[1], 
           cor = mean(cors, na.rm=TRUE), 
           min = min(cors, na.rm=TRUE), 
           max = max(cors, na.rm=TRUE))
  }) %>%
  kable(digits = 2)
```

# Filtering analysis

As described by Melanie in an email 8/2/16.

*Step 1: Select items that meet the following criteria only*

- Accent: 1-2 only.
- Naturalness: 4-7 only
- IDS/ADS: 1-3 or 5-7 only (as appropriate)
- Noise: 1-3 (or should we be more strict? Given these were all selected to be pretty noise-free to begin with, 1-3 might be sufficient)

*Step 2: Match across IDS and ADS on similarity for:*

- Approximate quantity (in duration) of contribution from a given mom
- Quantity of mentions of familiar objects, and unfamiliar objects (or try to match by specific object label?)

*Step 3: Re-check according some criteria of "sameness" (not sure what that should be)* 

- Accent, naturalness and noise level are similar between IDS and ADS and we haven't created a systematic bias in Step 2.

```{r}
filtered <- d %>%
  group_by(condition, register, object, baby_id, recording_id, file) %>%
  summarize(rating = mean(rating)) %>%
  spread(condition, rating) %>%
  filter(accent < 3, naturalness > 4, noise < 4,
         (register == "IDS" & idsness > 4) | (register == "ADS" & idsness < 4))

filtered
```

Output. 

```{r}
write_csv(filtered, "../wavs/filtered_and_normed.csv")
```

